One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-07 doc/genesetdp.tex
some results for Q10,20,30

\begin{figure}[htb]
	\begin{center}
    \begin{tabular}{c@{}c@{}c}
      \includegraphics[width=5cm]{figures/score_distribuition.png} &
      \includegraphics[width=5cm]{figures/score_distribuition.png} &
      \includegraphics[width=5cm]{figures/score_distribuition.png} \\
      $Q=10$ & $Q=20$ & $Q=30$ \\
    \end{tabular}
	\end{center}
  {\em FIXME: update these figures.}
  \caption{{\bf Score distribution of a query size of 10, 20 and 30 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

>>>>

\begin{figure}[htb]
	\begin{center}
    \begin{tabular}{c@{}c@{}c}
      \includegraphics[width=5cm]{figures/score_distribuition_Q10.png} &
      \includegraphics[width=5cm]{figures/score_distribuition_Q20.png} &
      \includegraphics[width=5cm]{figures/score_distribuition_Q30.png} \\
      $Q=10$ & $Q=20$ & $Q=30$ \\
    \end{tabular}
	\end{center}
  {\em FIXME: update these figures.}
  \caption{{\bf Score distribution of a query size of 10, 20 and 30 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}
